Prediction of 2024 US election ...

### 2024-11-04 paper/paper.qmd
fixed error in string

state_colors <- c(
  alabama = "red",
  arizona = ifelse((swing_state_predictions %>% 
                        filter(state == "Arizona") %>% 
                        select(winner)) == "TRUMP", "red", "blue"),
  arkansas = "red",
  california = "blue",
  colorado = "blue",
  connecticut = "blue",
  delaware = "blue",
  `district of columbia` = "blue",
  florida = ifelse((swing_state_predictions %>% 
                        filter(state == "Florida") %>% 
                        select(winner)) == "TRUMP", "red", "blue"),
  georgia = ifelse((swing_state_predictions %>% 
                        filter(state == "Georgia") %>% 
                        select(winner)) == "TRUMP", "red", "blue"),
  idaho = "red",
  illinois = "blue",
  indiana = "red",
  iowa = ifelse((swing_state_predictions %>% 
                        filter(state == "Iowa") %>% 
                        select(winner)) == "TRUMP", "red", "blue"),
  kansas = "red",
  kentucky = "red",
  louisiana = "red",
  maine = "gray",
  maryland = "blue",
  massachusetts = "blue",
  michigan = ifelse((swing_state_predictions %>% 
                        filter(state == "Michigan") %>% 
                        select(winner)) == "TRUMP", "red", "blue"),
  minnesota = ifelse((swing_state_predictions %>% 
                        filter(state == "Minnesota") %>% 
                        select(winner)) == "TRUMP", "red", "blue"),
  mississippi = "red",
  missouri = "red",
  montana = "red",
  nebraska = "gray",
  nevada = ifelse((swing_state_predictions %>% 
                        filter(state == "Nevada") %>% 
                        select(winner)) == "TRUMP", "red", "blue"),
  `new hampshire` = ifelse((swing_state_predictions %>% 
                        filter(state == "New Hampshire") %>% 
                        select(winner)) == "TRUMP", "red", "blue"),
  `new jersey` = "blue",
  `new mexico` = "blue",
  `new york` = "blue",
  `north carolina` = ifelse((swing_state_predictions %>% 
                        filter(state == "North Carolina") %>% 
                        select(winner)) == "TRUMP", "red", "blue"),
  `north dakota` = "red",
  ohio = ifelse((swing_state_predictions %>% 
                        filter(state == "Ohio") %>% 
                        select(winner)) == "TRUMP", "red", "blue"),
  oklahoma = "red",
  oregon = "blue",
  pennsylvania = ifelse((swing_state_predictions %>% 
                        filter(state == "Pennsylvania") %>% 
                        select(winner)) == "TRUMP", "red", "blue"),
  `rhode island` = "blue",
  `south carolina` = "red",
  `south dakota` = "red",
  tennessee = "red",
  texas = ifelse((swing_state_predictions %>% 
                        filter(state == "Texas") %>% 
                        select(winner)) == "TRUMP", "red", "blue"),
  utah = "red",
  vermont = "blue",
  virginia = ifelse((swing_state_predictions %>% 
                        filter(state == "Virginia") %>% 
                        select(winner)) == "TRUMP", "red", "blue"),
  washington = "blue",
  `west virginia` = "red",
  wisconsin = ifelse((swing_state_predictions %>% 
                        filter(state == "Wisconsin") %>% 
                        select(winner)) == "TRUMP", "red", "blue"), 
  wyoming = "red")

@@

>>>>

state_colors <- c(
  alabama = "red",
  arizona = ifelse((swing_state_predictions %>% 
                        filter(state == "Arizona") %>% 
                        select(winner)) == "Trump", "red", "blue"),
  arkansas = "red",
  california = "blue",
  colorado = "blue",
  connecticut = "blue",
  delaware = "blue",
  `district of columbia` = "blue",
  florida = ifelse((swing_state_predictions %>% 
                        filter(state == "Florida") %>% 
                        select(winner)) == "Trump", "red", "blue"),
  georgia = ifelse((swing_state_predictions %>% 
                        filter(state == "Georgia") %>% 
                        select(winner)) == "Trump", "red", "blue"),
  idaho = "red",
  illinois = "blue",
  indiana = "red",
  iowa = ifelse((swing_state_predictions %>% 
                        filter(state == "Iowa") %>% 
                        select(winner)) == "Trump", "red", "blue"),
  kansas = "red",
  kentucky = "red",
  louisiana = "red",
  maine = "gray",
  maryland = "blue",
  massachusetts = "blue",
  michigan = ifelse((swing_state_predictions %>% 
                        filter(state == "Michigan") %>% 
                        select(winner)) == "Trump", "red", "blue"),
  minnesota = ifelse((swing_state_predictions %>% 
                        filter(state == "Minnesota") %>% 
                        select(winner)) == "Trump", "red", "blue"),
  mississippi = "red",
  missouri = "red",
  montana = "red",
  nebraska = "gray",
  nevada = ifelse((swing_state_predictions %>% 
                        filter(state == "Nevada") %>% 
                        select(winner)) == "Trump", "red", "blue"),
  `new hampshire` = ifelse((swing_state_predictions %>% 
                        filter(state == "New Hampshire") %>% 
                        select(winner)) == "Trump", "red", "blue"),
  `new jersey` = "blue",
  `new mexico` = "blue",
  `new york` = "blue",
  `north carolina` = ifelse((swing_state_predictions %>% 
                        filter(state == "North Carolina") %>% 
                        select(winner)) == "Trump", "red", "blue"),
  `north dakota` = "red",
  ohio = ifelse((swing_state_predictions %>% 
                        filter(state == "Ohio") %>% 
                        select(winner)) == "Trump", "red", "blue"),
  oklahoma = "red",
  oregon = "blue",
  pennsylvania = ifelse((swing_state_predictions %>% 
                        filter(state == "Pennsylvania") %>% 
                        select(winner)) == "Trump", "red", "blue"),
  `rhode island` = "blue",
  `south carolina` = "red",
  `south dakota` = "red",
  tennessee = "red",
  texas = ifelse((swing_state_predictions %>% 
                        filter(state == "Texas") %>% 
                        select(winner)) == "Trump", "red", "blue"),
  utah = "red",
  vermont = "blue",
  virginia = ifelse((swing_state_predictions %>% 
                        filter(state == "Virginia") %>% 
                        select(winner)) == "Trump", "red", "blue"),
  washington = "blue",
  `west virginia` = "red",
  wisconsin = ifelse((swing_state_predictions %>% 
                        filter(state == "Wisconsin") %>% 
                        select(winner)) == "Trump", "red", "blue"), 
  wyoming = "red")

@@

```
Maine CD-2	47.40416	49.31394	Trump
Nebraska CD-2	49.90928	42.17853	Harris
